\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-30 notes/2loopNLSM.tex
A few more sentences on nonlocal.

As a first attempt at such a tame non-local representation,

\begin{itemize}
\item Recap assumptions of \cite{Bern:2015ooa}
\item Going beyond ``Feynman-type counting'' $\to$ 10010 initial
  ansatz.  Compare post-(sym+GI) on BCJ basis.
\item Discuss which cuts still fail.  Double check these statements
  \item Attempt at non-local.  Still have problems with cuts+syms+jacobi
  \end{itemize}

>>>>

As a first attempt at such a non-local representation, we consider
allowing one factor each of $s$,$t$, or $u$ in the denominator of each
of the double-box and penta-triangle numerators, in addition to the
standard local ansatze.  In order to not over-count the local terms,
we restrict the non-local ansatze to only truly rational terms, \eg
for the term $n_{\text{nl}}\sim \frac{x}{s}$ we drop all terms with
$x \propto s$.  Thus each basis diagram ansatz contains 114,422 terms
to start, 10,010 from the local terms and 34,804 from each of the
three non-local pieces.

\begin{itemize}
  \item Attempt at non-local.  Still have problems with cuts+syms+jacobi
  \end{itemize}
